Setup_OMs

### 2023-09-22 Ecov_study/catchability/Setup_OMs.Rmd
Update comments as OM/EM setup code transitioned to Catchability_ecov_sims.Rmd

-   B-H stock-recruit (for now)

@@

@@

-   Fishing history = F_MSY for 40 year history OR fish 2.5\*F_MSY for
    20 years than fish at F_MSY for remaining 20 - NOT CURRENTLY IMPLEMENTED, IN PROGRESS

@@

# 3) May run sensitivity run with no ecov effect in OM but compare same EMs
Check that ecov effect = 0 is essentially turning off ecov
```{r}
# Catchability set up
q_Ecov <- c("includeEcov", "excludeEcov") # May want to include these as a sensitivity run to compare what happens if OM has no ecov effect but EM assumes there is one (ecov process setup won't matter since fitting to data without effect specified in model)

@@

Use project 0 make_om() to set up generic OM input then add additional ecov settings afterwards before fitting model
- By default catchability impacted by environment only for fall (2nd) index
- Each OM stored in a corresponding folder/directory

>>>>

@@

-   Fishing history = F_MSY for 40 year history OR fish 2.5\*F_MSY for
    20 years than fish at F_MSY for remaining 20

@@

@@

# 3) May run sensitivity run with no ecov effect in OM but compare same EMs
Check that ecov effect = 0 is essentially turning off ecov = yes this is already implemented in step 1 outlined above
```{r}
# Catchability set up
q_Ecov <- c("includeEcov", "excludeEcov") # May want to include these as a sensitivity run to compare what happens if OM has no ecov effect but EM assumes there is one (ecov process setup won't matter since fitting to data without effect specified in model)

@@

Use unique copy of make_om() to set up generic OM input then add additional ecov settings afterwards before fitting model
- By default catchability impacted by environment only for fall (2nd) index
- Each OM stored in a corresponding folder/directory
